
%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ruby C. Sullivan \linebreak she/her}
\address{620 Park Ave \linebreak STE 259 \linebreak Rochester, NY 14607}
\contacts{(251) 586-2749 \linebreak ruby@stuffby.cc}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Work Experience}
		\begin{cvsubsection}{QA Engineer, Contractor}{Kodak Alaris}{Fall 2021 -- Present}
				
			\begin{itemize}
				\item Member of the sub-set of the Firmware/Hardware Quality Assurance team tasked with instituting changes to form and process of test cases including automation.
				\item Responsible for Firmware DSP Automation testing execution and reporting including refactoring reporting to work with testing tools.
				\item Backup within Firmware/Hardware Quality Assurance Team for Image Quality DevIQ testing.
			\end{itemize}
		\end{cvsubsection}
			
		\begin{cvsubsection}{Researcher, Co-op}{Simone Center, RIT}{Spring 2021}
				
			\begin{itemize}
				\item Performed customer discovery and product validation for a technology education start-up.
				\item Team lead for a group of student researchers from a variety of science and engineering backgrounds.
				\item Responsible for creating and delivering technical and investment presentations.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Co-op}{Bryx, Inc.}{Summer 2016 -- Winter 2016}	
			\begin{itemize}
				\item Responsible for designing and developing new web-based applications for first responders.
				\item Member of the Development team tasked with maintaining public website and performing level 1-2 tech support.
				\item Personal project laid the groundwork for a new product.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Lead Coding Instructor}{ICanCode Club}{Winter 2015 -- Fall 2017}		
			\begin{itemize}
				\item Taught students 1st-12th grade the basics of programming with the use of game design, robotics, and animation.
				\item Created and distributed curriculum for 100+ students in both short-term and long-term lesson programs.
				\item Listened to and incorporated the needs of students and parents into individualized lesson plans.
			\end{itemize}
		\end{cvsubsection}	
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Rochester, NY}{Rochester Institute of Technology}{August 2014 -- May 2021}
			\begin{itemize}
				\item B.S. in Computer Science w/ Minor in Software Engineering | Honors: Magna Cum Laude
				\item \textbf{Major Coursework:} Concepts of Computer Systems; Software Engineering Foundations; Programming \\Language Concepts; Analysis of Algorithms; Cryptography; Data Communication \& Networks; Data \\Management; Parallel \& Distributed Systems; Data Mining; Data Cleaning \& Preparation
				\item \textbf{Minor Coursework:} Software Process \& Project Management; Engineering of Software Subsystems; Human Centered Requirements \& Design; Web Engineering
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Volunteer (2016-present):} Organized and/or volunteered for multiple charity speedrunning events, such as Games Done Quick, RPG Valkyries, Speedruns 4 Trans Liberation, and Power Up With Pride.
				\item \textbf{Alumnus, Computer Science House (2014-present):} Living learning community focusing on technology and professional development at Rochester Institute of Technology.
				\item \textbf{President's Recognition, ASMS (2014):} One of 6 students to receive a distinction from the school president at graduation. Received recognition due to academic drive and technological aptitude.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Java; Javascript; React; jQuery; Python; C; Ruby on Rails; JSON; XML; LaTeX
				\item Visual Studio; MySQL; MATLAB; Microsoft Excel macros; pandas; qTest; Jira; Node.js; NodeCG; Gatsby; Jekyll
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
